A publishing infrastructure for AI-assisted academic authoring

### 2023-12-21 latex/manuscript.tex
latex: update manuscript from markdown

The tradition of scholarly manuscripts dates back thousands of years, evolving significantly with the advent of scientific journals approximately 350 years ago {[}\protect\hyperlink{ref-F3iZfGUC}{1}{]}.
External peer review, which is used by many journals, is even more recent, having been around for less than 100 years {[}\protect\hyperlink{ref-1HMhNrQq1}{2}{]}.
Most manuscripts are written by humans or teams of humans working together to describe new advances, summarize existing literature, or argue for changes in the status quo.
However, scholarly writing is a time-consuming process where results of a study are presented using a specific style and format.
Academics can sometimes be long-winded in getting to key points, making writing more impenetrable to their audience {[}\protect\hyperlink{ref-19YWsShi0}{3}{]}.

>>>>

The tradition of scholarly writing dates back thousands of years, evolving significantly with the advent of scientific journals approximately 350 years ago {[}\protect\hyperlink{ref-F3iZfGUC}{1}{]}.
External peer review, which is used by many journals, is even more recent, having been around for less than 100 years {[}\protect\hyperlink{ref-1HMhNrQq1}{2}{]}.
Most manuscripts are written by humans or teams of humans working together to describe new advances, summarize existing literature, or argue for changes in the status quo.
However, scholarly writing is a time-consuming process where results of a study are presented using a specific style and format.
Academics can sometimes be long-winded in getting to key points, making writing more impenetrable to their audience {[}\protect\hyperlink{ref-19YWsShi0}{3}{]}.
